Case study validations of automatic bullet matching

### 2018-09-28 index.Rmd
comment out dframe line

signatures <- read.csv("data/signatures.csv")
signatures <- dframe %>% select(bullet, land, sigs) %>% tidyr::unnest()
signatures %>% 
  ggplot(aes(x = x/1000)) + 
  geom_line(aes(y = raw_sig), colour = "grey70") +
  geom_line(aes(y = sig), colour = "grey30") +
  facet_grid(bullet~land) +
  ylim(c(-5,5)) +
  theme_bw() +
  ylab("Surface measurement (in microns)") +
  xlab("Relative Location (in millimeters)") 
```

>>>>

signatures <- read.csv("data/signatures.csv")
# signatures <- dframe %>% select(bullet, land, sigs) %>% tidyr::unnest()
signatures %>% 
  ggplot(aes(x = x/1000)) + 
  geom_line(aes(y = raw_sig), colour = "grey70") +
  geom_line(aes(y = sig), colour = "grey30") +
  facet_grid(bullet~land) +
  ylim(c(-5,5)) +
  theme_bw() +
  ylab("Surface measurement (in microns)") +
  xlab("Relative Location (in millimeters)") 
```
